---
title: "Sultans Of Statistics MGT256 Project"
output: html_notebook
---

MGT256 - Project for House Pricing

```{r}
housing_data_main <- read.csv("2018-property-sales-data.csv")

head(housing_data_main)

is.na(housing_data_main)

which(is.na(housing_data_main))

col_missing <- colSums(is.na(housing_data_main))

# Code to remove certain columns
housing_data_cleaned <- housing_data_main[, !(names(housing_data_main) %in% c("Taxkey", "Address", "CondoProject", "Nbhd", "Style"))]

housing_data_cleaned <- housing_data_cleaned[!(housing_data_cleaned$PropType == "Vacant Land"), ]

library(dplyr)

# Define a function to categorize materials
# categorize_material <- function(material) {
#   durable_materials <- c("Brick", "Stone", "Fiber-Cement")
#   
#   if (material %in% durable_materials) {
#     return("Durable Materials")
#   } else {
#     return("Non-Durable Materials")
#   }
# }
# 
# housing_data_cleaned <- mutate(housing_data_cleaned, Material_Category = sapply(housing_data_cleaned$material_column, categorize_material))

housing_data_cleaned <- housing_data_cleaned %>%
  mutate(material_category = case_when(
    Extwall %in% c("Brick", "Stone", "Fiber-Cement") ~ "Durable Materials",
    Extwall %in% c("Aluminum / Vinyl", "Block", "Frame", "Masonry / Frame", "Prem Wood", "Stucco") ~ "Non-Durable Materials",
    TRUE ~ "Other"
  ))


housing_data_cleaned_cat <- housing_data_cleaned %>%
  mutate(residential_var = case_when(PropType == "Residential" ~ 1, TRUE ~ 0),
         commercial_var = case_when(PropType == "Commercial" ~ 1, TRUE ~ 0),
         condo_var3 = case_when(PropType == "Condominium" ~ 1, TRUE ~ 0))

# Note - We can also make a column called as durability, and 

head(housing_data_cleaned_cat)
```


```{r}
# Install and load necessary packages
install.packages(c("tidyverse", "corrplot"))
library(tidyverse)
library(corrplot)

# Load your data
# Assuming your data is in a CSV file named 'property_data.csv'
data <- read.csv('property_data.csv')

# Display the first few rows of the dataset
head(data)

# Explore the dataset
# Summary statistics
summary(data)

# Check for missing values
sum(is.na(data))

# Visualize correlations between variables
correlation_matrix <- cor(data[, c('Sales_Price', 'Year_built', 'Fin_Sqft', 'Units', 'Bdrms', 'Fbath', 'Hbath', 'Lot_Size')])
corrplot(correlation_matrix, method="color")

# Visualize the distribution of the dependent variable (Sales_Price)
hist(data$Sales_Price, main='Distribution of Sales Price', xlab='Sales Price', col='skyblue', border='black')

# Visualize relationships between Sales_Price and numerical predictor variables
numeric_vars <- c('Year_built', 'Fin_Sqft', 'Units', 'Bdrms', 'Fbath', 'Hbath', 'Lot_Size')
for (var in numeric_vars) {
  plot(data[, var], data$Sales_Price, main=paste('Relationship between', var, 'and Sales Price'), xlab=var, ylab='Sales Price', col='blue', pch=19)
}

# Visualize relationships between Sales_Price and categorical predictor variables
categorical_vars <- c('PropertyType', 'Style', 'ExtWall')
for (var in categorical_vars) {
  boxplot(data$Sales_Price ~ data[, var], main=paste('Relationship between', var, 'and Sales Price'), xlab=var, ylab='Sales Price', col='lightblue', border='black')
}

```



```{r}
# Scatterplot matrix for numerical predictor variables
data_for_scatters <- readxl::read_excel("2018-property-sales-data.xlsx", sheet = "regression_all_proptype")

numeric_vars <- c('Year_built', 'Fin_sqft', 'Units', 'Bdrms', 'Fbath', 'Hbath', 'Lot_size', 'Sale_price')
plotnew <- pairs(data_for_scatters[, numeric_vars], col=c('red', 'orange'), pch = 16, cex = 1.5)library(GGally)
library(ggplot2)

# ggpairs(data_for_scatters)




# Bar plot for categorical variables
categorical_vars <- c('PropertyType', 'Style', 'ExtWall')
par(mfrow=c(1, length(categorical_vars)), mar=c(4, 4, 2, 1))
for (i in 1:length(categorical_vars)) {
  counts <- table(data[, categorical_vars[i]])
  barplot(counts, main=categorical_vars[i], col='lightblue', border='black', ylim=c(0, max(counts) + 10))
}

# Time series plot for Sale_Date
data_for_scatters$Sale_Date <- as.Date(data$Sale_Date, format='%Y-%m-%d')
plot(data$Sale_Date, data$Sales_Price, type='l', col='blue', xlab='Sale Date', ylab='Sales Price', main='Time Series Plot of Sales Price')

# Boxplot of Sales_Price by Nbhd
boxplot(data$Sales_Price ~ data$Nbhd, main='Sales Price by Neighborhood', xlab='Neighborhood', ylab='Sales Price', col='lightblue', border='black', las=2)

```


```{r}
# Correlation plot with ggplot2
library(ggplot2)
correlation_data <- cor(data[, c('Sales_Price', 'Year_built', 'Fin_Sqft', 'Units', 'Bdrms', 'Fbath', 'Hbath', 'Lot_Size')])
correlation_data_long <- as.data.frame(as.table(correlation_data))
names(correlation_data_long) <- c("Variable1", "Variable2", "Correlation")
correlation_plot <- ggplot(correlation_data_long, aes(x=Variable1, y=Variable2, fill=Correlation)) +
  geom_tile(color='white') +
  scale_fill_gradient2(low='blue', high='red', mid='white', midpoint=0, limit=c(-1,1), space="Lab", name="Correlation") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
print(correlation_plot)

# Density plots for numerical variables
par(mfrow=c(2, 4), mar=c(4, 4, 2, 1))
for (var in numeric_vars) {
  density_plot <- density(data[, var])
  plot(density_plot, main=paste('Density Plot of', var), col='blue', lwd=2)
}

for (i in cat_var) {
  repeat_frequency <- table(data_for_categorical$i)
  View(repeat_frequency)
  repeat_proportion <- prop.table(repeat_frequency)
  barplot(repeat_frequency)
  abline(h=0)
}

# Violin plots for Sales_Price by PropertyType and Bdrms
par(mfrow=c(1, 2), mar=c(4, 4, 2, 1))
violin_plot1 <- violinplot(Sales_Price ~ PropertyType, data=data, col='lightblue', border='black', main='Violin Plot of Sales Price by PropertyType')
violin_plot2 <- violinplot(Sales_Price ~ Bdrms, data=data, col='lightblue', border='black', main='Violin Plot of Sales Price by Bdrms')

# Pair plot using ggplot2 for numerical variables
numeric_vars_no_sale_price <- setdiff(numeric_vars, 'Sales_Price')
pair_plot <- ggplot(data, aes(x=Sales_Price, y=data[, numeric_vars_no_sale_price])) +
  geom_point() +
  geom_smooth(method='lm', col='blue') +
  labs(title='Pair Plot of Numerical Variables', x='Sales Price') +
  theme_minimal()
print(pair_plot)

```


```{r}

data_for_heatmap <- readxl::read_excel("2018-property-sales-data.xlsx", sheet = "regression_residential_only")

head(data_for_heatmap)

# Load necessary libraries
library(corrplot)

# Assuming your data is in a variable named 'data'
# Replace 'data' with your actual data frame

# Select relevant numerical columns for correlation analysis
numeric_vars <- c('Sale_price', 'Year_built', 'Fin_sqft', 'Units', 'Bdrms', 'Fbath', 'Hbath', 'Lot_size', 'material_num', 'Stories', 'Sale_month')

# Calculate correlation matrix
correlation_matrix <- cor(data_for_heatmap[, numeric_vars])

# Create a heatmap
corrplot(correlation_matrix, method="square", type="upper", tl.col="black", tl.srt=45)

```

```{r}
data_for_categorical <- readxl::read_excel("2018-property-sales-data.xlsx", sheet = "preregression_all_proptype")

cat_var <- c('PropType', 'Extwall', 'material_category')

hist(data_for_categorical$Sale_price, breaks = 1000000,xlim = c(10000, 1200000))
     # plot = TRUE, xlim = c(10000, 1200000))

num_var 

boxplot(data_for_categorical$Sale_price)


# for (i in cat_var) {
# repeat_frequency <- table(data_for_categorical$PropType)
# View(repeat_frequency)
# repeat_proportion <- prop.table(repeat_frequency)
# barplot(repeat_proportion, grid(col = "gray", lty = "dotted")
# )
# abline(h=0)
# Adding customizations
# title(main = "Customized Bar Plot", sub = "Subtitle")
# axis(side = 1, at = 1:length(categories), labels = categories, las = 2)  # Rotate x-axis labels
# axis(side = 2, las = 1)  # Ensure y-axis labels are horizontal
# grid(col = "gray", lty = "dotted")
# }
```

```{r}
data_for_categorical <- readxl::read_excel("2018-property-sales-data.xlsx", sheet = "preregression_all_proptype")

numeric_vars <- c('Fin_sqft', 'Units', 'Bdrms', 'Fbath', 'Hbath', 'Lot_size', 'Sale_price')

for (i in numeric_vars) {
  var <- data_for_categorical$i
  
  hist(data_for_categorical$var)
}
```

```{r}
data_for_all <- readxl::read_excel("2018-property-sales-data.xlsx", sheet = "preregression_all_proptype")

data_for_residential <- readxl::read_excel("2018-property-sales-data.xlsx", sheet = "preregression_residential_only")

data_agani <- data.frame(
  sales_price = data_for_all$Sale_price,
  Fin_sqft = data_for_all$Fin_sqft
)

boxplot(data_for_all$Fin_sqft, col = c("skyblue", "lightgreen", "lightcoral"), main = "Boxplots for Different Variables")
summary(data_for_all$Fin_sqft)
```

summary statistics of variables all proptypes : - 

```{r}
data_for_all <- readxl::read_excel("2018-property-sales-data.xlsx", sheet = "preregression_all_proptype")

data_for_residential <- readxl::read_excel("2018-property-sales-data.xlsx", sheet = "preregression_residential_only")

summary(data_for_residential$Fin_sqft)
summary(data_for_residential$Lotsize)
summary(data_for_residential$Stories)
summary(data_for_residential$Bdrms)
summary(data_for_residential$Fbath)
summary(data_for_residential$Hbath)
summary(data_for_residential$Sale_price)

boxplot(data_for_residential$Bdrms, data_for_residential$Stories, data_for_residential$Fbath, data_for_residential$Hbath, data_for_residential$Units, labels)



boxplot(data_for_residential$Lotsize)
boxplot(data_for_residential$Stories)
boxplot(data_for_residential$Bdrms)
boxplot(data_for_residential$Fbath)
boxplot(data_for_residential$Hbath)
boxplot(data_for_residential$Sale_price) #mot important new slide
```
All proptypes : 


```{r}
options(scipen = 999)

data_for_all <- readxl::read_excel("2018-property-sales-data.xlsx", sheet = "regression_all_proptype")

data_for_all$residential_num <- as.factor(data_for_all$residential_num)
data_for_all$commercial_num <- as.factor(data_for_all$commercial_num)
data_for_all$condominium_num <- as.factor(data_for_all$condominium_num)

model_1 <- lm(Sale_price~residential_num+commercial_num+condominium_num+material_num+Stories+Nr_of_rms+Fin_sqft+Units, data = data_for_all)
summary(model_1
        )

model_2 <- lm(Sale_price~residential_num+commercial_num+condominium_num+material_num+Stories+Nr_of_rms+Fin_sqft+Units+Bdrms+Fbath+Hbath+Sale_month, data = data_for_all)
summary(model_2)

model_3 <- lm(Sale_price~residential_num+commercial_num+condominium_num+material_num+Stories+Nr_of_rms+Units+Bdrms+Fbath+Hbath+Lot_size+Sale_month, data = data_for_all)
summary(model_3)

model_4 <- lm(Sale_price~residential_num+commercial_num+condominium_num+material_num+Stories+Nr_of_rms+Fin_sqft+Units+Lot_size+Sale_month, data = data_for_all)
summary(model_4)

print(AIC(model_1))
print(AIC(model_2))
print(AIC(model_3))
print(AIC(model_4))

#model 4 is most accurate

data_for_all %>% dplyr::mutate_all(as.factor) %>% str

stepModel <- step(model_4)


```

```{r}
library(caret)
model_5 <- train(Sale_price ~ ., data = data_for_all, method = "lm")
important_features <- varImp(model_5)
selected_features <- predict(important_features, data_for_all)

library(randomForest)
model_6 <- randomForest(Sale_price ~ ., data = data_for_all)
importance_m6 <- importance(model_6)
selected_features <- rownames(importance_m6[importance_m6$MeanDecreaseGini > threshold, ])

class(importance_m6)

model_7 <- lm(Sale_price ~ poly(Fin_sqft, degree = 2)+Stories+Nr_of_rms+Units+Bdrms+Fbath+Hbath+Lot_size+Sale_month, data = data_for_all)
summary(model_7)


model_8 <- lm(Sale_price ~ poly(Fin_sqft, degree = 3)+Stories+Nr_of_rms+Units+Bdrms+Fbath+Hbath+Lot_size+Sale_month+residential_num+commercial_num+condominium_num+material_num, data = data_for_all)
summary(model_8)

model_9 <- lm(Sale_price ~ poly(Fin_sqft, degree = 3)+Stories+Nr_of_rms+Units+Bdrms+Fbath+Hbath+Lot_size+Sale_month+residential_num*commercial_num*condominium_num*material_num, data = data_for_all)
summary(model_9)



AIC(model_7b)
AIC(model_7c)
AIC(model_8)
AIC(model_9)

model 8 or model 9 is the best fit for now

```


Residential Only :-

```{r}
options(scipen = 999)

data_for_all <- readxl::read_excel("2018-property-sales-data.xlsx", sheet = "regression_residential_only")

model_1 <- lm(Sale_price~Stories+Fin_sqft+Units+material_num, data = data_for_all)
summary(model_1
        )

model_2 <- lm(Sale_price~material_num+Stories+Fin_sqft+Units+Bdrms+Fbath+Hbath+Lot_size+Sale_month, data = data_for_all)
summary(model_2)

model_3 <- lm(Sale_price~material_num+Stories+Units+Bdrms+Fbath+Hbath+Lot_size+Sale_month, data = data_for_all)
summary(model_3)

model_4 <- lm(Sale_price~material_num+Stories+Fin_sqft+Units+Lot_size+Sale_month, data = data_for_all)
summary(model_4)

print(AIC(model_1))
print(AIC(model_2))
print(AIC(model_3))
print(AIC(model_4))

data_for_all %>% dplyr::mutate_all(as.factor) %>% str

stepModel <- step(model_4)

#model 3 is good for now



library(caret)
model_5 <- train(Sale_price ~ ., data = data_for_all, method = "lm")
important_features <- varImp(model_5)
selected_features <- predict(important_features, data_for_all)

library(randomForest)
model_6 <- randomForest(Sale_price ~ ., data = data_for_all)
importance_m6 <- importance(model_6)
selected_features <- rownames(importance_m6[importance_m6$MeanDecreaseGini > threshold, ])

class(importance_m6)

model_7 <- lm(Sale_price ~ poly(Fin_sqft, degree = 2)+Stories+Units+Bdrms+Fbath+Hbath+Lot_size+Sale_month, data = data_for_all)
summary(model_7)

# got adjusted R^2 as 50percent when i took a variable with the slope of 105 (which is way lesser as a contributor)

model_7b <- lm(Sale_price ~ poly(Bdrms, degree = 2)+Stories+Units+Fin_sqft+Fbath+Hbath+Lot_size+Sale_month+material_num, data = data_for_all)
summary(model_7b)

model_7c <- lm(Sale_price ~ poly(Bdrms, degree = 3)+Units+Lot_size+Bdrms+Sale_month+Fbath*Hbath*Fin_sqft, data = data_for_all)
summary(model_7c)


model_8 <- lm(Sale_price ~ Fin_sqft+Stories+Units+Bdrms*Fbath*Hbath+Lot_size+Sale_month+material_num, data = data_for_all)
summary(model_8)

model_9 <- lm(Sale_price ~ poly(Units, degree = 2)+Stories+Units+Bdrms*Fbath*Hbath+material_num, data = data_for_all)
summary(model_9)

model_9a <- lm(Sale_price ~ poly(Fbath*Fin_sqft, degree = 2)+Stories*Units+Bdrms+Hbath+material_num+Lot_size, data = data_for_all)
summary(model_9a)

# model 7c gives us the best results for now

AIC(model_7)
AIC(model_7b)
AIC(model_7c)
AIC(model_8)
AIC(model_9)
AIC(model_9a)


```

H0 = coefficient is zero
Ha = coefficient is not zero

if p-value is very less , that means we have good evidence that the coefficient is not zero, and we have statistical evidence that it contributes to the equation / linear model / linear equation

if p-value is 0.15 that means 15 percent undr the curve area, it means that we cannot say with confidence that the coeffienct is NOT 0, very less evidence, therefore that is not contributing too much, because we dont know for sure its not 0.



KNN

1. for all proptypes

```{r}
data_for_all_proptype <- readxl::read_excel("2018-property-sales-data.xlsx", sheet = "regression_all_proptype")

train_valid_data_index <- sample(nrow(data_for_all_proptype), size=nrow(data_for_all_proptype)*0.90, replace=F)

data_for_all_train_valid <- data_for_all_proptype[train_valid_data_index,]
data_for_all_test <- data_for_all_proptype[-train_valid_data_index,]

library(caret)
myCtrl <- trainControl(method="cv",
                       number=10)
myGrid <- expand.grid(.k=c(1:15))
set.seed(1)
knn_data_for_all <- train(as.numeric(Sale_price)~., 
                 data=data_for_all_train_valid,
                 method="knn",
                 trControl=myCtrl,
                 tuneGrid=myGrid,
                 preProc=c("center","scale"))

knn_data_for_all

predicted_prices <- predict(knn_data_for_all,
        newdata=data_for_all_test,
        type='raw') # We are predicting a numerical variable
forecast::accuracy(predicted_prices,data_for_all_test$Sale_price)
```

2. for residential only

```{r}
data_for_all_proptype <- readxl::read_excel("2018-property-sales-data.xlsx", sheet = "regression_residential_only")

# data_for_all_proptype <- readxl::read_excel("2018-property-sales-data.xlsx", sheet = "regression_all_proptype")

train_valid_data_index <- sample(nrow(data_for_all_proptype), size=nrow(data_for_all_proptype)*0.90, replace=F)

data_for_all_train_valid <- data_for_all_proptype[train_valid_data_index,]
data_for_all_test <- data_for_all_proptype[-train_valid_data_index,]

library(caret)
myCtrl <- trainControl(method="cv",
                       number=10)
myGrid <- expand.grid(.k=c(1:15))
set.seed(1)
knn_data_for_all <- train(as.numeric(Sale_price)~., 
                 data=data_for_all_train_valid,
                 method="knn",
                 trControl=myCtrl,
                 tuneGrid=myGrid,
                 preProc=c("center","scale"))

knn_data_for_all

predicted_prices <- predict(knn_data_for_all,
        newdata=data_for_all_test,
        type='raw') # We are predicting a numerical variable
forecast::accuracy(predicted_prices,data_for_all_test$Sale_price)
```


After removing outliers : - 

LM residential - 

```{r}
options(scipen = 999)

data_for_all <- readxl::read_excel("no_outliers_2018-property-sales-data.xlsx", sheet = "regression_residential_only")

model_1 <- lm(Sale_price~Stories+Fin_sqft+Units+material_num, data = data_for_all)
summary(model_1
        )

model_2 <- lm(Sale_price~material_num+Stories+Fin_sqft+Units+Bdrms+Fbath+Hbath+Lot_size+Sale_month, data = data_for_all)
summary(model_2)

model_3 <- lm(Sale_price~material_num+Stories+Units+Bdrms+Fbath+Hbath+Lot_size+Sale_month, data = data_for_all)
summary(model_3)

model_4 <- lm(Sale_price~material_num+Stories+Fin_sqft+Units+Lot_size+Sale_month, data = data_for_all)
summary(model_4)

print(AIC(model_1))
print(AIC(model_2))
print(AIC(model_3))
print(AIC(model_4))

data_for_all %>% dplyr::mutate_all(as.factor) %>% str

stepModel <- step(model_4)




library(caret)
model_5 <- train(Sale_price ~ ., data = data_for_all, method = "lm")
important_features <- varImp(model_5)
selected_features <- predict(important_features, data_for_all)

library(randomForest)
model_6 <- randomForest(Sale_price ~ ., data = data_for_all)
importance_m6 <- importance(model_6)
selected_features <- rownames(importance_m6[importance_m6$MeanDecreaseGini > threshold, ])

class(importance_m6)

model_7 <- lm(Sale_price ~ poly(Fin_sqft, degree = 2)+Stories+Units+Bdrms+Fbath+Hbath+Lot_size+Sale_month, data = data_for_all)
summary(model_7)

# got adjusted R^2 as 50percent when i took a variable with the slope of 105 (which is way lesser as a contributor)

model_7b <- lm(Sale_price ~ poly(Bdrms, degree = 2)+Stories+Units+Fin_sqft+Fbath+Hbath+Lot_size+Sale_month+material_num, data = data_for_all)
summary(model_7b)

model_7c <- lm(Sale_price ~ poly(Bdrms, degree = 2)+Units+Lot_size+Bdrms+Sale_month+Fbath*Hbath*Fin_sqft, data = data_for_all)
summary(model_7c)


model_8 <- lm(Sale_price ~ Fin_sqft+Stories+Units+Bdrms*Fbath*Hbath+Lot_size+Sale_month+material_num, data = data_for_all)
summary(model_8)

model_9 <- lm(Sale_price ~ poly(Units, degree = 2)+Stories+Units+Bdrms*Fbath*Hbath+material_num, data = data_for_all)
summary(model_9)

model_9a <- lm(Sale_price ~ poly(Fbath*Fin_sqft, degree = 2)+Stories*Units+Bdrms+Hbath+material_num+Lot_size, data = data_for_all)
summary(model_9a)
```




```{r}
options(scipen = 999)

library(caret)

set.seed(123)

data_for_all <- readxl::read_excel("2018-property-sales-data.xlsx", sheet = "regression_all_proptype")

data_for_all$residential_num <- as.factor(data_for_all$residential_num)
data_for_all$commercial_num <- as.factor(data_for_all$commercial_num)
data_for_all$condominium_num <- as.factor(data_for_all$condominium_num)


# Create an index for training and testing sets
set.seed(1) # for reproducability
training_index <- sample(nrow(data_for_all),
                         size= nrow(data_for_all)*0.8)


train_data <- data_for_all[training_index,]
test_data <- data_for_all[-training_index,]

model_1 <- lm(Sale_price~residential_num+commercial_num+condominium_num+material_num+Stories+Nr_of_rms+Fin_sqft+Units, data = train_data)
summary(model_1
        )

model_2 <- lm(Sale_price~residential_num+commercial_num+condominium_num+material_num+Stories+Nr_of_rms+Fin_sqft+Units+Bdrms+Fbath+Hbath+Sale_month, data = train_data)
summary(model_2)

model_3 <- lm(Sale_price~residential_num+commercial_num+condominium_num+material_num+Stories+Nr_of_rms+Units+Bdrms+Fbath+Hbath+Lot_size+Sale_month, data = train_data)
summary(model_3)

model_4 <- lm(Sale_price~residential_num+commercial_num+condominium_num+material_num+Stories+Nr_of_rms+Fin_sqft+Units+Lot_size+Sale_month, data = train_data)
summary(model_4)

print(AIC(model_1))
print(AIC(model_2))
print(AIC(model_3))
print(AIC(model_4))

model_7 <- lm(Sale_price ~ poly(Fin_sqft, degree = 2)+Stories+Nr_of_rms+Units+Bdrms+Fbath+Hbath+Lot_size+Sale_month, data = train_data)
summary(model_7)


model_8 <- lm(Sale_price ~ poly(Fin_sqft, degree = 3)+Stories+Nr_of_rms+Units+Bdrms+Fbath+Hbath+Lot_size+Sale_month+residential_num+commercial_num+condominium_num+material_num, data = train_data)
summary(model_8)

model_9 <- lm(Sale_price ~ poly(Fin_sqft, degree = 3)+Stories+Nr_of_rms+Units+Bdrms+Fbath+Hbath+Lot_size+Sale_month+residential_num*commercial_num*condominium_num*material_num, data = train_data)
summary(model_9)



AIC(model_7b)
AIC(model_7c)
AIC(model_8)
AIC(model_9)

predicted_prices <- predict(model_9, test_data)
head(predicted_prices)

library(forecast)

print(forecast::accuracy(predicted_prices, test_data$Sale_price))

```


```{r}
options(scipen = 999)

library(caret)

set.seed(123)

data_for_residential_only <- readxl::read_excel("2018-property-sales-data.xlsx", sheet = "regression_residential_only")


# Create an index for training and testing sets
set.seed(1) # for reproducability
training_index <- sample(nrow(data_for_residential_only),
                         size= nrow(data_for_residential_only)*0.8)


residential_train_data <- data_for_residential_only[training_index,]
residential_test_data <- data_for_residential_only[-training_index,]

model_1 <- lm(Sale_price~material_num+Stories+Fin_sqft+Units, data = residential_train_data)
summary(model_1
        )

model_2 <- lm(Sale_price~material_num+Stories+Fin_sqft+Units+Bdrms+Fbath+Hbath+Sale_month, data = residential_train_data)
summary(model_2)

model_3 <- lm(Sale_price~material_num+Stories+Units+Bdrms+Fbath+Hbath+Lot_size+Sale_month, data = residential_train_data)
summary(model_3)

model_4 <- lm(Sale_price~material_num+Stories+Fin_sqft+Units+Lot_size+Sale_month, data = residential_train_data)
summary(model_4)

print(AIC(model_1))
print(AIC(model_2))
print(AIC(model_3))
print(AIC(model_4))

model_7 <- lm(Sale_price ~ poly(Fin_sqft, degree = 2)+Stories+Units+Bdrms+Fbath+Hbath+Lot_size+Sale_month, data = residential_train_data)
summary(model_7)


model_8 <- lm(Sale_price ~ poly(Fin_sqft, degree = 3)+Stories+Units+Bdrms+Fbath+Hbath+Lot_size+Sale_month+material_num, data = residential_train_data)
summary(model_8)

model_9 <- lm(Sale_price ~ poly(Fin_sqft, degree = 3)+Stories+Units+Bdrms+Fbath+Hbath+Lot_size+Sale_month+material_num, data = residential_train_data)
summary(model_9)



AIC(model_7b)
AIC(model_7c)
AIC(model_8)
AIC(model_9)

predicted_prices <- predict(model_9, residential_test_data)
head(predicted_prices)

library(forecast)

print(forecast::accuracy(predicted_prices, residential_test_data$Sale_price))
```


